From Likes to Change: Assessing the Impact of Citizen Engagement on the European

### 2023-06-17 Article.Rmd
Corrected article

    Cristina-Dana Popescu (Orcid ID: ) is a Lecturer at the Faculty of Letters, the Faculty of Law and Administrative Sciences and at the Faculty of Mathematics and Informatics at Ovidius University in Constanta. She holds a Bachelor’s degree in Philology at the University of Bucharest, the Faculty of Foreign Languages and Literatures, English and German Department, a Master's degree in Philosophy at the University “Al. I. Cuza”, Iaşi, Romania and a Ph.D. in Philology - British and American Literature, at the University “Al. I. Cuza”, Iaşi, Romania. She has been teaching English since 1999 being also a School Director for 12 years of a private High School in Constanta, she is an accomplished teacher with demonstrated ability to teach, motivate and direct students while maintaining high interest and achievement. She holds the Excellence Award within the Faculty of Letters, as the winner of the Performance in Education Competition at Ovidius University in Constanta. She also holds internationally recognized trainings in the field of psychology, being a licensed NLP Practitioner at the International Association for Neuro-Linguistic Programming and also a licensed of Silva Method, the Immersion Silva Life and Intuition System at Silva International Headquarters, Laredo, Texas, USA. She also holds the qualification of Trainer, COR Code 242401, certified by SC Training & Teaching Center, București.With over 30 scientific articles published in specialized journals at national and international conferences, author of ISI and BDI articles, participant both in CNCSIS grant teams and in University Projects as Expert in the Study Programs Pillars and Expert in Educational Material Development and also author of 3 books and co-author of 1 book in the field of literature and various specialized languages, she has demonstrated her expertise in the academic field.

abstract: |
  This study investigates the role of emotional resonance in social media  communications from the European Commission (EC) and its impact on public participation across various platforms including Facebook, Instagram, Twitter, and YouTube. Findings  indicate that emotionally resonant communications significantly enhance public engagement, with variations depending on the specific platform. Both positive and negative emotional resonance significantly impact participation, with the latter having a more pronounced  effect. Our research highlights the critical importance of platform-specific strategies and the incorporation of emotional resonance in public communications to foster participation in policy dialogues. An analysis of the engagement rates and sentiment across platforms reveals unique tonal variations in the EC's discourse. The effect of emotional resonance on public engagement is also found to be moderated by the choice of social media platform, with certain platforms more significantly moderating the relationship between emotional resonance and engagement than others. This study lays the groundwork for refining communication strategies within a multi-platform   digital governance environment.

@@

```{r analysis-preferences, echo=FALSE}
# Seed for random number generation
  set.seed(44542)
  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Introduction
\justify
In recent years, the rise of social media platforms has led to significant changes in the way institutions, including public organizations, communicate with their audiences. As a result, the importance of citizen engagement in the process of communication through social media has become increasingly recognized. This engagement involves not only a one-way flow of information from public institutions to citizens, but also an interactive dialogue between the two parties.

The concept of engagement in social media has been studied extensively in recent years, with researchers exploring various aspects of this phenomenon. One such study, conducted by @Dolan2016, approached social media engagement behavior from a uses and gratifications perspective, focusing on the motivations and benefits that users derive from engaging with social media. Meanwhile, the study by @Dragseth2020 explored how social media can be used to build engagement among students in the context of political science education.

Another important aspect of engagement in social media is the role it plays in activation campaigns aimed at consumers. @Mirbagheri2019 conceptualized and developed a scale to measure consumers' engagement with social media activation campaigns. Additionally, @Smith2015 analyzed public engagement with organizations through social media, highlighting the importance of two-way communication between public institutions and citizens.

The differentiating role of platform type in engagement with social media and social media advertising was explored by @Voorveld2018, who found that the level of engagement varies across different social media platforms.

In addition to understanding the various aspects of engagement in social media, it is also important to recognize the significance of citizen engagement in the context of public institutions. Citizen engagement plays a critical role in ensuring transparency and accountability in public decision-making processes. Furthermore, engagement with citizens can lead to the development of more effective policies and programs that better serve the needs of the community.

Moreover, the importance of citizen engagement in the process of communication through social media cannot be overstated. Through social media, public institutions can engage in an interactive dialogue with citizens, build trust, and develop more effective policies and programs. As such, further research, and exploration of the concept of engagement in social media is critical for ensuring that public institutions continue to effectively communicate with and serve the needs of their communities.

Citizen engagement through social media can also contribute to the empowerment of individuals and groups, giving them a voice in public decision-making processes and enabling them to hold public institutions accountable for their actions. This can help to build stronger, more resilient communities that are better equipped to respond to challenges and opportunities.

@@

Overall, the rise of social media has transformed the way public institutions communicate with citizens, placing a greater emphasis on engagement and two-way communication. Understanding the various aspects of engagement in social media is critical for public institutions to effectively communicate with and serve the needs of their communities. By leveraging the power of social media to engage with citizens, public institutions can build trust, empower individuals and groups, and develop more effective policies and programs that better serve the needs of the community.

## Literature review
In studying the impact of citizen engagement on the European Commission's social media platforms, it is crucial to discern the key concepts that underpin this research. These concepts are engagement, social media platforms, and sentiment analysis, which form the backbone of many academic discourses that revolve around these themes.

@@

The significance of engagement reaches a higher dimension in the political and public sphere. With social media platforms becoming an integral part of contemporary political communication [@flewPopulismGlobalisationSocial2020; @krzyzanowskiDigitalDiplomacyPolitical2020], citizen engagement has become paramount, as seen in the activities of European Union (EU) agencies [@Muller2022]. There is a myriad of ways in which citizens engage with politics on social media, from commenting on posts to sharing and liking content [@DeWilde2022]. This interaction has been correlated with a spectrum of outcomes, such as influencing voting behavior [@marquartThisTimeNot2020] and attitudes towards vaccination [@mascheriniSocialMediaUse2022].

Simultaneously, social media platforms are becoming recognized as powerful tools for promoting and managing engagement. This dual role is exemplified in the case of the European Commission's activities in Romania [@Rus2021]. Recognizing the potential of these platforms to facilitate citizen engagement, EU institutions have taken steps to optimize their use, implementing various strategies [@Bene2022; @Kanol2021; @ozdemirBirdEyeView2022].

In assessing the impact of citizen engagement on the EU's social media platforms, researchers employ an assortment of methods, one of which is sentiment analysis. This approach, which involves the systematic identification and categorization of the emotional tone behind words, aims to gauge public sentiment, attitudes, and emotions towards specific topics [@Wei2021]. It has been applied in diverse contexts, such as analyzing the emotional distribution in EU smart city communication [@kowalikSocialMediaDistribution2021] and exploring public opinions on climate change policy [@Wei2021].

@@

To sum up, understanding the impact of citizen engagement on the European Commission's social media platforms is a multifaceted issue. These platforms offer opportunities for meaningful citizen engagement and public communication, but their influence is dictated by a complex interplay of individual behavior, institutional strategy, societal trends, and technological developments. This complexity calls for a nuanced understanding of each constituent factor and their collective role in shaping the landscape of citizen engagement within the context of the European Commission's social media platforms. It is a call to researchers, policymakers, and practitioners to continuously explore this evolving realm to maximize the benefits of citizen engagement while mitigating its potential pitfalls.

# The present study
Relying on the theoretical framework previously described, the present study aimed to investigate public engagement across various official European Commission social media platforms (Facebook, Instagram, Twitter, and YouTube). We also compared and contrasted the patterns, trends, and characteristics of online user interactions and responses across these platforms. Translating these aims into research questions (RQs), the present study investigated the following:

- *RQ~1~*. How is the communication with emotional resonance associated with higher public engagement levels?
- *RQ~2~*. Does social media platforms influences the emotional resonance on public engagement?
- *RQ~3~*. Does social media platforms moderates the effect of emotional resonance on public engagement?

@@

The novelty of our study lies in the fact that we have systematically compared and contrasted user engagement and emotional resonance across multiple social media platforms utilized by the European Commission. While previous research has generally focused on the impact of citizen engagement within a single social media platform, our study is unique in its comprehensive cross-platform analysis.

In this context, we have pursued an integrated approach to understanding how emotional resonance can influence public engagement levels across these platforms. Furthermore, we have explored the moderating effect of the social media platform itself on the impact of emotional resonance, a novel aspect that has not been fully addressed in previous research.

The innovative approach of this study allowed us to draw robust conclusions about the nuanced relationship between communication strategy, emotional resonance, platform choice, and public engagement. Our research has therefore not only provided key insights into the patterns of citizen engagement on European Commission's social media platforms, but also presented an advanced framework for understanding how such engagement can be effectively harnessed and maximized for public outreach and policymaking.

@@

The initial assumptions assessment was performed by descriptive univariate analysis, data screening for outliers, and missing cases analysis, to verify univariate normality. We further conducted a sentiment analysis, and, finally a linear moderated regression was used for hypothesis testing.

@@

```{r sentiment, echo=FALSE, include=FALSE}
  source("02 - Sentiment analysis.R")
```
```{r, boxplot-EXT, out.width = '510px', fig.align='center', fig.cap='Boxplot of engagement rates on social media channels. Extremes included', warning=FALSE}
  bp.ext
```
```{r, sent-EXT, out.width = '510px', fig.align='center', fig.cap='Sentiment analysis chart on social media channels. Extremes included', warning=FALSE}
  st.ext
```
```{r, boxplot-NEXT, out.width = '510px', fig.align='center', fig.cap='Boxplot of engagement rates on social media channels. Extremes excluded', warning=FALSE}
  bp.next
```
```{r, sent-NEXT, out.width = '510px', fig.align='center', fig.cap='Sentiment analysis chart on social media channels. Extremes excluded', warning=FALSE}
  st.next
```
## Sentiment analysis
A comprehensive sentiment analysis was conducted on data, both with (see Fig. \@ref(fig:boxplot-EXT) and Fig. \@ref(fig:sent-EXT)) and without extreme outliers (see Fig. \@ref(fig:boxplot-NEXT) and Fig. \@ref(fig:sent-NEXT)) suggesting distinctive tonal variations in the discourse employed by the European Commission across different social media platforms.

@@

The main effect of negative emotional resonance was statistically significant *(B=`r m3.neg.B`, t=`r m3.neg.t`, p  `r m3.neg.p`, \(\beta\)=`r m3.neg.Bt`)*, but not the main effect of positive emotional resonance *(B=`r m3.poz.B`, t=`r m3.poz.t`, p  `r m3.poz.p`, \(\beta\)=`r m3.poz.Bt`)*, and both were moderated by social network. Furthermore, compared to Twitter influence, Facebook *(B=`r m3.Fbk.B`, t=`r m3.Fbk.t`, p  `r m3.Fbk.p`, \(\beta\)=`r m3.Fbk.Bt`)* and Youtube *(B=`r m3.Yut.B`, t=`r m3.Yut.t`, p  `r m3.Yut.p`, \(\beta\)=`r m3.Yut.Bt`)* were statistically significant positively associated with engagement rate, but not Instragram *(B=`r m3.Ins.B`, t=`r m3.Ins.t`, p  `r m3.Ins.p`, \(\beta\)=`r m3.Ins.Bt`)*.

@@

Compared to Twitter posts, if the messages with positive emotional resonance were posted on Instagram or Youtube, the engagement rate increased statistically significant and the effect was most powerfull on Instagram than on Youtube. No interaction effect was observed on Facebook related on positive emotional resonance *(B=`r m3.PozFbk.B`, t=`r m3.PozFbk.t`, p  `r m3.PozFbk.p`, \(\beta\)=`r m3.PozFbk.Bt`)*

# Discussion
The current study embarked on an investigative journey to examine public engagement across a range of social media platforms utilized by the European Commission, laying specific emphasis on the impact of emotional resonance within disseminated content. The vital role of social media in communication strategies of public institutions has been widely recognized [@Smith2015], accentuating the necessity for an in-depth comprehension of the dynamics of engagement.

@@

Despite these findings, the study is not without limitations. The scope of this research was confined to the European Commission's use of four primary social media platforms. Future inquiries could potentially explore other platforms or public institutions to determine the universality of the observed patterns. Furthermore, while our focus lay primarily on emotional resonance, future research could delve into other aspects of communication, such as tone, complexity, and framing.

@@

To conclude, this study underscores the imperative role of both emotional resonance and platform-specific norms in propelling public engagement on social media. The ability to establish an emotional connection with the audience, made possible through well-conceived and executed posts, emerges as a powerful tool for amplifying engagement levels. Such engagement is not merely about expanding the reach or visibility of public institutions like the European Commission, but is a mechanism for fostering a dynamic and participatory relationship between these institutions and the citizens they serve.

@@

To conclude, this study underscores the significance of emotional resonance and platform-specific norms in driving public engagement. It suggests that forming an emotional connection with the audience through posts could amplify engagement levels. By understanding these dynamics, public institutions like the European Commission can refine their social media strategies, enhance citizen engagement, and bolster the efficacy of their public communication. Despite the limitations, the study provides a valuable starting point for future research into the multifaceted world of social media engagement.
\newpage

>>>>

    Cristina-Dana Popescu (Orcid ID: https://orcid.org/0009-0009-5280-6608) is a Lecturer at the Faculty of Letters, the Faculty of Law and Administrative Sciences and at the Faculty of Mathematics and Informatics at Ovidius University in Constanta. She holds a Bachelor’s degree in Philology at the University of Bucharest, the Faculty of Foreign Languages and Literatures, English and German Department, a Master's degree in Philosophy at the University “Al. I. Cuza”, Iaşi, Romania and a Ph.D. in Philology - British and American Literature, at the University “Al. I. Cuza”, Iaşi, Romania. She has been teaching English since 1999 being also a School Director for 12 years of a private High School in Constanta, she is an accomplished teacher with demonstrated ability to teach, motivate and direct students while maintaining high interest and achievement. She holds the Excellence Award within the Faculty of Letters, as the winner of the Performance in Education Competition at Ovidius University in Constanta. She also holds internationally recognized trainings in the field of psychology, being a licensed NLP Practitioner at the International Association for Neuro-Linguistic Programming and also a licensed of Silva Method, the Immersion Silva Life and Intuition System at Silva International Headquarters, Laredo, Texas, USA. She also holds the qualification of Trainer, COR Code 242401, certified by SC Training & Teaching Center, București.With over 30 scientific articles published in specialized journals at national and international conferences, author of ISI and BDI articles, participant both in CNCSIS grant teams and in University Projects as Expert in the Study Programs Pillars and Expert in Educational Material Development and also author of 3 books and co-author of 1 book in the field of literature and various specialized languages, she has demonstrated her expertise in the academic field.

abstract: |
  This research undertakes an examination of the function that emotional resonance plays in the social media communications disseminated by the European Commission (EC) and its subsequent influence on public involvement across a multitude of platforms such as Facebook, Instagram, Twitter, and YouTube. The findings of this research underscored that communications laden with emotional resonance considerably amplify public engagement, though the magnitude of this amplification is dependent on the individual platform. Furthermore, both positive and negative forms of emotional resonance exhibit a noteworthy influence on public participation. However, it has been observed that the impact of negative emotional resonance is more distinct and profound. Our research underscored the pivotal significance of employing strategies tailored to specific platforms and integrating emotional resonance into public communications as a means to stimulate participation in policy discourse.An analytical examination of both engagement rates and sentiment across various platforms unveils distinctive tonal nuances within the European Commission's discourse.

The impact of emotional resonance on public engagement is noted to be contingent upon the specific social media platform employed, as certain platforms demonstrate a more pronounced moderating effect on the association between emotional resonance and engagement relative to others. This research provided the foundational framework for the enhancement of communicative strategies within a multi-platform digital governance environment comprising multiple platforms.

@@

```{r analysis-preferences, echo=FALSE}
# Seed for random number generation
  set.seed(44542)
  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Introduction
\justify
In recent years, it has been observed that the ascendance of social media platforms precipitated noteworthy transformations in the communication strategies employed by institutions, inclusive of public organizations, to engage with their respective audiences. Consequently, the significance of citizen participation in the process of communication mediated through social media platforms, gained escalated acknowledgment. This participatory process transcends the conventional one-directional dissemination of information from public bodies to citizens. Rather, it encapsulates an interactive discourse, fostering a two-way dialogue between the engaged parties.

The notion of engagement within the context of social media has been the subject of comprehensive scholarly investigation in recent years, with researchers delving into diverse facets of this phenomenon. One such study, conducted by @Dolan2016, scrutinized social media engagement behavior through the theoretical lens of the uses and gratifications paradigm, emphasizing the motivations and benefits users acquire from their interaction with social media platforms. Concurrently, an academic study undertaken by @Dragseth2020 probed the application of social media for fostering engagement among students, specifically within the field of political science education.

Another important aspect of engagement in social media pertains to its integral role in activation campaigns directed towards consumers. Mirbagheri et al. (2019) conceptualized and developed a scale to measure consumers' engagement with social media activation campaigns.  Complementarily, a comprehensive analysis conducted by Smith et al. (2015) scrutinized public engagement with organizations via social media channels, highlighting the importance of two-way communication between public institutions and citizens.
The distinctive role of platform type concerning engagement with social media and its corresponding advertising was examined meticulously by Voorveld et al. (2018). This research established that the magnitude of engagement diverges significantly across distinct social media platforms.

In addition to understanding the multifaceted dimensions of engagement within social media, it is of crucial importance to acknowledge the significance of citizen participation in the realm of public institutions. Citizen engagement is instrumental in guaranteeing transparency and accountability within public decision-making procedures. Furthermore, the proactive engagement of citizens can facilitate the formulation of efficacious policies and initiatives that are more adept at meeting the requirements of the broader community.
Moreover, the importance of citizen engagement in the process of communication through social media cannot be overstated. Through social media, public institutions can engage in an interactive dialogue with citizens, build trust, and develop more effective policies and programs. As such, further research, and exploration of the concept of engagement in social media is critical for ensuring that public institutions continue to effectively communicate with and serve the needs of their communities.

Citizen participation via social media platforms can further contribute to the empowerment of individuals and collective entities, effectively granting them a decisive voice in public decision-making processes and providing a mechanism for holding public institutions accountable for their actions. This empowerment strategy can potentially engender the construction of robust, resilient communities possessing enhanced capacities to navigate both challenges and opportunities.

@@

Overall, the rise of social media has transformed the way public institutions communicate with citizens, placing a greater emphasis on engagement and two-way communication. Understanding the various aspects of engagement in social media is critical for public institutions to effectively communicate with and serve the needs of their communities. By leveraging the power of social media to engage with citizens, public institutions can build trust, empower individuals and groups, and develop more effective policies and programs that effectively address the needs of the community.

## Literature review
In examining the influence of citizen engagement on the social media platforms of the European Commission, it is imperative to discern and elucidate the fundamental concepts that underlie this research. The concepts in question encompass engagement, social media platforms, and sentiment analysis, constituting the foundational pillars of numerous scholarly discussions centered around these topics.

@@

The significance of engagement reaches a higher dimension in the political and public sphere. With social media platforms becoming an integral part of contemporary political communication [@flewPopulismGlobalisationSocial2020; @krzyzanowskiDigitalDiplomacyPolitical2020], citizen engagement has become paramount, as seen in the activities of European Union (EU) agencies [@Muller2022]. There is a myriad of ways in which citizens engage with politics on social media, from commenting on posts to sharing and liking content [@DeWilde2022]. This interaction has been correlated with a variety of outcomes, including voting behaviour [@marquartThisTimeNot2020] and vaccination attitudes. [@mascheriniSocialMediaUse2022].

Simultaneously, social media platforms are becoming recognized as powerful tools for promoting and managing engagement. This dual functionality is exemplified through the case study of the European Commission's endeavors in Romania.[@Rus2021]. Recognizing the potential of these platforms to facilitate citizen engagement, EU institutions have taken steps to optimize their use, implementing various strategies [@Bene2022; @Kanol2021; @ozdemirBirdEyeView2022].

When evaluating the influence of citizen engagement on the social media platforms of the European Union, researchers utilize a variety of methodologies, including sentiment analysis. This approach entails a systematic process of identifying and categorizing the emotional undertones conveyed by textual expressions, with the objective of assessing public sentiment, attitudes, and emotions towards specific subjects.[@Wei2021]. It has been applied in diverse contexts, such as analyzing the emotional distribution in EU smart city communication [@kowalikSocialMediaDistribution2021] and exploring public opinions on climate change policy [@Wei2021].

@@

In conclusion, comprehending the impact of citizen engagement on the social media platforms of the European Commission encompasses a multifaceted matter. These platforms offer opportunities for substantive citizen engagement and public communication, yet their influence is contingent upon an intricate interplay of individual behavior, institutional strategy, societal trends, and technological advancements. This intricacy necessitates a nuanced comprehension of each constituent element and their collective contributions to shaping the landscape of citizen engagement within the context of the European Commission's social media platforms. Consequently, it calls upon researchers, policymakers, and practitioners to continuously explore this evolving domain in order to maximize the advantages of citizen engagement while mitigating potential drawbacks.

# The present study
Grounded in the aforementioned theoretical framework, the primary objective of the current research endeavour was to examine the extent of public engagement manifested on diverse official social media platforms employed by the European Commission. Specifically, this investigation encompassed platforms such as Facebook, Instagram, Twitter, and YouTube. Furthermore, the study sought to analyse and juxtapose the discernible patterns, trends, and distinctive attributes of online user interactions and responses observed within these platforms. In order to structure the inquiry, the research questions (RQs) that guided this investigation were as follows:

- *RQ~1~*. How is the communication with emotional resonance associated with higher public engagement levels?
- *RQ~2~*. Does social media platforms influence the emotional resonance on public engagement?
- *RQ~3~*. Does social media platforms moderates the effect of emotional resonance on public engagement?

@@

The novelty of our study lies in the fact that we have systematically compared and contrasted user engagement and emotional resonance across multiple social media platforms utilized by the European Commission. While previous research has typically focused on the impact of citizen engagement within a single social media platform, our comprehensive cross-platform analysis makes this study unique.

Within this context, we have pursued an integrated approach to comprehending the potential influence of emotional resonance on the levels of public engagement observed within these platforms. Furthermore, our investigation encompasses an exploration of the moderating influence exerted by the underlying social media platform on the impact of emotional resonance, a novel aspect that has not been thoroughly explored in prior research.

The pioneering methodology implemented in this research allowed us to draw robust conclusions concerning the intricate interplay between communication strategy, emotional resonance, selection of platform, and public engagement. Consequently, our research has not only provided critical understanding of the modalities of citizen engagement on the social media platforms employed by the European Commission, but also proposed an advanced paradigm for comprehending how such engagement can be effectively harnessed and optimized for public outreach and policymaking.

@@

The initial assumptions assessment was performed by descriptive univariate analysis, data screening for outliers, and missing cases analysis, to verify univariate normality. An additional layer of sentiment analysis was carried out to provide a more comprehensive understanding. Lastly, a moderated linear regression model was used as the methodological tool for hypothesis testing.

@@

```{r sentiment, echo=FALSE, include=FALSE}
  source("02 - Sentiment analysis.R")
```
```{r, boxplot-EXT, out.width = '510px', fig.align='center', fig.cap='Boxplot of engagement rates on social media channels. Extremes included', warning=FALSE}
  bp.ext
```
```{r, sent-EXT, out.width = '510px', fig.align='center', fig.cap='Sentiment analysis chart on social media channels. Extremes included', warning=FALSE}
  st.ext
```
```{r, boxplot-NEXT, out.width = '510px', fig.align='center', fig.cap='Boxplot of engagement rates on social media channels. Extremes excluded', warning=FALSE}
  bp.next
```
```{r, sent-NEXT, out.width = '510px', fig.align='center', fig.cap='Sentiment analysis chart on social media channels. Extremes excluded', warning=FALSE}
  st.next
```
## Sentiment analysis
An exhaustive sentiment analysis was conducted on the dataset, considering scenarios with and without extreme outliers, as illustrated in Figure @ref(fig:sent-NEXT)). This analysis suggested distinctive tonal variations employed by the European Commission across different social media platforms.

@@

The main effect of negative emotional resonance emerged as statistically significant *(B=`r m3.neg.B`, t=`r m3.neg.t`, p  `r m3.neg.p`, \(\beta\)=`r m3.neg.Bt`)*, contrasting with the main effect of positive emotional resonance which did not manifest the same significance.  *(B=`r m3.poz.B`, t=`r m3.poz.t`, p  `r m3.poz.p`, \(\beta\)=`r m3.poz.Bt`)*Both effects were observed to be moderated by the underlying social network. Furthermore, in comparison to the influence on Twitter, both Facebook and YouTube exhibited statistically significant positive associations with the engagement rate, a phenomenon not witnessed with Instagram.*(B=`r m3.Ins.B`, t=`r m3.Ins.t`, p  `r m3.Ins.p`, \(\beta\)=`r m3.Ins.Bt`)*.

@@

Contrasting with Twitter posts, communications imbued with positive emotional resonance exhibited a statistically significant increase in engagement rate when disseminated on Instagram or YouTube, with the effect manifesting more potently on Instagram relative to YouTube. Notably, no interaction effect correlating with positive emotional resonance was observed on the Facebook platform. *(B=`r m3.PozFbk.B`, t=`r m3.PozFbk.t`, p  `r m3.PozFbk.p`, \(\beta\)=`r m3.PozFbk.Bt`)*

# Discussion
The present research undertook a detailed exploration to examine public engagement across an array of social media platforms implemented by the European Commission, with particular attention dedicated to the influence of emotional resonance within the disseminated content. The paramount role of social media within the communication strategies of public institutions has been extensively acknowledged [@Smith2015], thus underscoring the exigency for a profound understanding of the intricacies of engagement dynamics.

@@

Notwithstanding the above findings, it is essential to recognize the inherent limitations of this study. The scope of this research was confined to the European Commission's use of four primary social media platforms. Future inquiries could potentially explore other platforms or public institutions to determine the universality of the observed patterns. Furthermore, while our focus lay primarily on emotional resonance, future research could delve into other aspects of communication, such as tone, complexity, and framing.

@@

To conclude, this study underscores the imperative role of both emotional resonance and platform-specific norms in propelling public engagement on social media. The ability to establish an emotional connection with the audience, made possible through well-conceived and executed posts, emerges as a powerful tool for amplifying engagement levels. Such engagement transcends mere augmentation of reach or visibility of public institutions, such as the European Commission, and represents a conduit for cultivating a dynamic and interactive association between these institutions and the citizenry they serve.

@@

In conclusion, this study accentuates the paramount importance of emotional resonance and platform-specific norms in stimulating public engagement. The findings infer that the formation of an emotional bond with the audience through meticulously constructed posts may serve to magnify the levels of engagement. By understanding these dynamics, public institutions like the European Commission can refine their social media strategies, enhance citizen engagement, and bolster the efficacy of their public communication. Despite the limitations, the study provides a valuable starting point for future research into the multifaceted world of social media engagement.
\newpage
